### 2015-11-13 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
aufgabe 2 fast fertig und aufgabe 3 fertig

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
\usepackage{color}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{grffile} %allows to use pngs
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
\usepackage{cite}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

@@

\subsection*{How to get infinite solutions with t and s?}
The equation influence by t and s is:

\begin{equation*}
max: s*x_1+t*x_2
\end{equation*}

\noindent way to get an infinite solution could be to generate a endless loop with values for s and t like:
\begin{eqnarray*}
s=s*x_1\label{inf1}\\ 
t=t*x_2 \label{inf2}\\ 
or\\
s=t*x_2\label{inf3}\\ 
t=s*x_1 \label{inf4}\\ 
\end{eqnarray*}

\subsection*{how to get the points?}

@@

%\newpage
%\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
%\bibliographystyle{ieeetr}

>>>>

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
\usepackage{color}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{grffile} %allows to use pngs
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
\usepackage{cite}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

@@

\subsection*{How to get infinite solutions with t and s?}
The linear program has infinite solutions, if we assign the following values to s and t:

\begin{align}
 s &= x_2 \nonumber \\
 t &= -x_1 \nonumber \\
\end{align}

\noindent These values would lead to the equation $x_2*x_1 + (-x_1)*x_2$, which is always zero. So 
the maximal result is zero and you can fill in arbitrary numbers to get this result, i.e. infinite 
solutions.

\subsection*{how to make the points a optimal solution?}

@@

The Carrillo-Lipman bound is defined by $B_{pq} \coloneqq B(A) - (\sum_{i<j} s(\hat{A}_i, \hat{A}_j)-s(\hat{A}_p,\hat{A}_q))$, 
where $B(A)$ is a score for the alignment computed by a heuristic and $s(\hat{A}_i,\hat{A}_j)$ is 
the score of a optimal alignment of sequences $i$ and $j$. If we have just two sequences $p$ and $q$, 
this equation would be simplified as 
\[
B_{pq} = B(A) - (s(\hat{A}_p,\hat{A}_q)-s(\hat{A}_p,\hat{A}_q)) = B(A).
\]

\noindent So the Carrillo-Lipman bound for two sequences is just the computed score by a heuristic.
%\newpage
%\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
%\bibliographystyle{ieeetr}
